### 2020-06-02 writeup/proof_examples.tex
minor

%For the case $\sigma_1^2=\sigma_2^2=\sigma^2$, 
We define the function
\begin{align}
	\val(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
%\cor Under the setting of Lemma \ref{prop_model_shift_tight}, 
For the isotropic model with $\sigma_1^2=\sigma_2^2=\sigma^2$, using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that $\val(\hat{B}; w_1, w_2)= \val(v) \cdot \left( 1+\OO(p^{-1/2+\e})\right)$. Hence the validation loss in \eqref{approxvalid} reduces to
\be\label{boundv-w}
\wt f(\hat B; v)=\left[N_2\cdot \val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
\ee
with high probability for any constant $\e>0$. \nc Thus for the following discussions, it suffices to focus on the behavior of $\val (v)$. Let $\hat w$ the minimizer of $\val(v)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that $\hat{w}$ is close to $1$, and then \eqref{boundv-w} implies that $\hat v$ is also close to 1.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result. 
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
For the isotropic model, the minimizer for $\val(v)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{whp}\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof. First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

@@

Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get whp,
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
\end{align}
In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. With estimate \eqref{eq_isometric}, we see that 
$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
Hence we need to choose that $p\cdot d^2 \sim \sigma^2$. On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$. The above considerations lead to the choices of parameters in \eqref{choiceofpara}. Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\ 
&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
\end{align}
whp for some constant $\e>0$.

@@

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of it) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that 
 \be\label{var-beta}\te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
	\[  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \]
Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$, it gives the first statement of Proposition \ref{prop_dist_transition}.

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
	\[ \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \]
which gives the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

\subsection{Supplement to Section \ref{sec_data_size}} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

\begin{proof}[Proof of Proposition \ref{prop_data_size}]
Following the above proof of Proposition \ref{prop_dist_transition}, we get from \eqref{upper101} that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
\be\label{pos1}
pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

For the first statement of Proposition \ref{prop_data_size}, we notice that the function
$$\frac1{ \Phi(\rho_1, \rho_2)}=\frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}=(\rho_2-1) \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)^{-1} $$
is strictly increasing with respect to $\rho_1$ as long as $\rho_2> 2$. In particular, by taking $\rho_1\to \infty$, we get the bound:
$$\frac{\rho_1(\rho_1+\rho_2)(\rho_2-1)}{(\rho_1+\rho_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  (\rho_2-1) \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4.$$
Hence as long as we take 
 $$pd^2  \le \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
 then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp. Plugging into $\rho_1>50$, we obtain the first statement.

The two bounds in the second statement follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
\be\label{trivialphi}
\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2} \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
\ee

@@

\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality
\begin{align}\label{pos1solv}
 & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <\sigma^2\cdot (1-\oo(1)) .
 \end{align}
 then we can solve \eqref{pos1solv} to get
 $$\rho_1 < \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1+\rho_1^{-1/2})^4 (\rho_2 - 1)\cdot (1+\oo(1))  - \sigma^2}  .$$
 %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
 Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.

@@

%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  =: \delta_\beta(M)+ g_{\vari}(M),

@@

%where $(a_1,a_2)$ satisfies \eqref{eq_a12extra}. On the other hand, by Theorem \ref{thm_model_shift} we can estimate $\delta_\beta$ as

@@

%&\left| \delta_{\beta}(M_0) - \frac{d^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \tr\left[\Sigma_1^{1/2}{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\Sigma_1^{1/2}\right]\right| \le \delta + \OO(p^{1-\e}d^2),

>>>>

%For the case $\sigma_1^2=\sigma_2^2=\sigma^2$, 
We define the function
\begin{align}
	\val(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
%\cor Under the setting of Lemma \ref{prop_model_shift_tight}, 
For the isotropic model with $\sigma_1^2=\sigma_2^2=\sigma^2$, using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that $\val(\hat{B}; w_1, w_2)= \val(v) \cdot \left( 1+\OO(p^{-1/2+\e})\right)$. Hence the validation loss in \eqref{approxvalid} reduces to
\be\label{boundv-w}
\wt f(\hat B; v)=\left[N_2\cdot \val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
\ee
with high probability for any constant $\e>0$. \nc Thus for the following discussions, it suffices to focus on the behavior of $\val (v)$. Let $\hat w$ the minimizer of $\val(v)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that $\hat{w}$ is close to $1$, and then \eqref{boundv-w} implies that $\hat v$ is also close to 1.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_2^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result. 
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
For the isotropic model, the minimizer for $\val(v)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{whp}\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof. First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

@@

Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get whp,
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
\end{align}
In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. With estimate \eqref{eq_isometric}, we see that 
$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
Hence we need to choose that $p\cdot d^2 \sim \sigma^2$. On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$. The above considerations lead to the choices of parameters in \eqref{choiceofpara}. Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to
\begin{align}
\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\ 
&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
\end{align}
whp for some constant $\e>0$.

@@

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of it) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\bias} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\bias}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\bias} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that 
 \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$, it gives the first statement of Proposition \ref{prop_dist_transition}.

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper102} to
	\be\label{neg1} \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
which gives the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

\subsection{Supplement to Section \ref{sec_data_size}} \label{app_proof_32}
We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.

\begin{proof}[Proof of Proposition \ref{prop_data_size}]
Following the above proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ whp if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ whp if \eqref{neg1} holds. 
%\be\label{pos1}
%pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
%and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
%\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

We first explain the meaning of the condition 
\be\label{explainpsi}\Psi(\beta_1,\beta_2)>2/(\rho_2-1).\ee 
%For the first statement of Proposition \ref{prop_data_size}, we 
Notice that the function
$$ \Phi(\rho_1, \rho_2)=\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}=\frac{1}{\rho_2-1} \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)$$
is strictly decreasing with respect to $\rho_1$ as long as $\rho_2> 2$, and $ \Phi(\rho_1, \rho_2)$ converges to $(\rho_2-1)^{-1}$ as $\rho_1\to \infty$.  Moreover, we notice that $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$. Hence \eqref{explainpsi} implies that \eqref{neg1} holds for all  large enough $\rho_1$. The transition from positive transfer when $\rho_1$ is small to negative transfer when $\rho_1$ is large is described by the two bounds in Proposition \ref{prop_data_size}.

% $$ \Psi(\beta_1,\beta_2) \ge \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
% then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp. Plugging into $\rho_1>50$, we obtain the first statement. ...... Note that for $\rho_1>40$, we have 
%$\gamma_+^{-1}$

The two bounds follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
\be\label{trivialphi}
\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le  \Phi(\rho_1, \rho_2) \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
\ee

@@

\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality:
\begin{align}\label{pos1solv}
 &  \Psi(\beta_1,\beta_2) \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}   < \gamma_+^{-1} .
 \end{align}
 then we can solve \eqref{pos1solv} to get
 \be\label{addconstraint}\rho_1 < \frac{\rho_2-2}{\Psi(\beta_1,\beta_2) \cdot \gamma_+ (\rho_2 - 1) - 1}  .\ee
 %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
 This gives the first statement of Proposition \ref{prop_data_size}. %Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.

 Note that if we require the RHS of \eqref{addconstraint} to be larger than $40$, that is, \eqref{addconstraint} is not a null condition. Then together with \eqref{explainpsi}, we get
 $$ \rho_2 - 2>( 2\gamma_+ -1)\rho_1 .$$
Plugging into $\rho_1>40$, we get $\rho_2 \ge 106$. This gives a constraint on $\rho_2$.

@@

%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  =: \delta_{\bias}(M)+ g_{\vari}(M),

@@

%where $(a_1,a_2)$ satisfies \eqref{eq_a12extra}. On the other hand, by Theorem \ref{thm_model_shift} we can estimate $\delta_{\bias}$ as

@@

%&\left| \delta_{\bias}(M_0) - \frac{d^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \tr\left[\Sigma_1^{1/2}{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\Sigma_1^{1/2}\right]\right| \le \delta + \OO(p^{1-\e}d^2),
